Proposal: Loose Grammar Inference for Lossy Compression

### 2012-10-18 proposal.tex
began evaluation section

There are two important metrics in evaluating our

>>>>

There are two important metrics we plan on evaluating our algorithm with. First,
the lossiness it introduces should allow it to compress very well. This can be
quantified by comparing its compression ratio with other grammar based and 
general compression schemes on text sources, especially semi-structured text 
which might best exhibit nearly hierarchical data.

We would also like to make use of our algorithm to reveal the inherent 
structure in text data. Our hope is that allowing lossiness will alow it 
to capture larger scale structures, so we plan on subjectively evaluating 
the CFGs produced for how well they group the components that a human
might perceive in pieces of text.

Comparing our runtime with existing algorithms can be done in a
straightforward way.

We plan on evaluating our algorithm on standard english prose texts, but
we also suspect that the texts which will prove most interesting to 
analyze are those with slightly more structure imposed on them. Human-made
tables such as the genealogical trees discussed in \cite{nevillphd} are a
good example, as are simple musical pieces. Slightly more artificial
examples we might try include strings generated from actual CFGs but with
small amounts of noise added in.
